%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{FullStack Engineer}
{Centene}
{Remote}
{May 2022 - July 2023}
{
\begin{cvitems}
\item {Supported on-going tickets and built features to meet business requiremen          ts using MongoDB, Golang, React, and PowerShell.}
\item {Developed software tools and made suggestions to increase work productivity.}
\item {Moved pagination logic from front end to backend and refactored database query, leading up to 5 times performance improvement in page load speed.}
\item {Created a tool in Go that scans source code to produce a verification program to ensure Go models matches database model in an effort of updates and data migration.}
\item {Identified potential performance bottleneck in a backend service and worked with teammates to resolve those issues.}
\item {Technology used: Go, React, MongoDB, Talend, Powershell}
\end{cvitems}
}

\cventry
{Software Engineer}
{T-Mobile}
{Remote}
{October 2020 - August 2021}
{
\begin{cvitems}
\item {During onboarding process, create a micro version of the internal payment system as for in a 3 person team hackathon.}
\item {Created a microservice as part of an ongoing process to implement Direct Debit, in effor to reduce existing banking fees, up to 7 figures savings.}
\item {Technology used: RabbitMQ, Cassandra, Java, Spring, Vue.js, Bulma, Go}
\end{cvitems}
}

\cventry
{Software Developer}
{Skillup Technologies}
{Remote}
{February 2020 - October 2020}
{
\begin{cvitems}
\item {Deployed customized Open edX solution, servikng clients such as DOD}
\item {Technology used: Django, Python, CSS, Go}
\end{cvitems}
}
 
\cventry
{Software Developer}
{Curio Inc}
{Remote}
{February 2019 - July 2019}
{
\begin{cvitems}
\item {Designed and created a staging database to reduce load time in fewtch data from API.}
\item {Designed API endpoints using Django, Python and PostgresSQL, resulting in a faster load time in fetch data for mobile app.}
\end{cvitems}
}


\cventry
{Software Developer} % Job title
{Curio Inc} % Organization
{Remote} % Location
{Feb 2017 - Oct 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Complete rewrite of Curio's mobile app in IOS and redesigned the backend api using Strongloop API framework that leads to 3x performance gain.}
\item {Optimized Curio's Postgresql SQL database structure and redesigned existing queries that leads to at least 3x quicker query time. }
\item {Designed an administration tool using Electron for batch data upload, dramatically increased the team's work flow and efficiency.}
\item {Screened and interviewed potential software developer candidates as an for the expansion of the team}  
\end{cvitems}
}

\cventry
{Software Developer} % Job title
{8Likes Inc} % Organization
{Redmond, WA} % Location
{July 2016 - Sept. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed "Review Analytics" feature to display product's review history data scraped from Amazon.com. Wrote SQL to query data from PostgreSQL for retrieving data using LoopBack and C3.js in displaying chart data. }
\item {Co-developed "Elite Group" major feature with engineering team and ensured that users has been successful charge using Stripe.}
\item {Implemented a ranking system algorithm in email campaign to select a variety of deals based on various factors.}
\item {Shipped production ready features and deployed to Amazon AWS.}  
\end{cvitems}
}


\cventry
{Software Lead} % Job title
{Dot Incorporation} % Organization
{Seoul, S.Korea} % Location
{Sept. 2014 - Apr. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Headed software development for both the mobile and web platforms in a 5 member start-up team.  Designed and built all software related products, providing information accessibility for visually impaired people.}
\item {Designed and built a Braille display demo using Arduino Mega board and 24 LED pins for a start-up competition held in Seoul to win additional funding. Programmed the demo to display Braille patterns in Korean, controlled by iPhone via Bluetooth.  Awarded 3rd place with \$10,000 funding.}
\item {Built a custom Braille input based instant messaging app on IOS, using MEAN stack and Socket.IO as back-end, and awarded first place in Golden Pentagon (South Korean version of Shark Tank) with \$1,100,000 additional funding.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Mobile Lead} % Job title
{Wagon Incorporation} % Organization
{Kirkland, WA} % Location
{Feb. 2014 - Aug. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Headed IOS mobile development at Wagon, connecting movers to users for moving difficult-to-carry furniture.}
\item {Redesigned the user interface and RESTful API call from a legacy Objective-C code base to our custom design, achieving a faster product launch time, resulting in a quicker product iteration and 50\% reduction in development time.}
\item {Collaborated and resolved a JavaScript bug in the Google Map API with the co-founder on the web platform, resulting in a more smoother user experience.}
\item {Discovered and resolved a critical bug where an API call not returning necessary data in JSON format.} 
\end{cvitems}
}


%------------------------------------------------

\cventry
{Software Lead/Co-founder} % Job title
{Pozz} % Organization
{Seattle, WA} % Location
{Dec. 2013 - Feb. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Showcased our Craigslist-like web app demo with a modernized user interface at "Hell Night", an annual entrepreneurship competition hosted at UW, winning "play money" from potential customers and receiving invaluable feedback.}
\item {Hand coded HTML, CSS, JQuery and utilized bootstrap framework along with to create the user interface for a quick prototype.}
\end{cvitems} 
}


%------------------------------------------------

\cventry
{Software Tester} % Job title
{Point Inside Incorporation} % Organization
{Bellevue, WA} % Location
{Aug. 2011 - Oct. 2011} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Tracked down and tested an average 50 bugs each month on the Android platform, reporting directly to the VP of Engineering, and promoted to managing all software related bugs on both IOS and Android platform on JIRA.}
\end{cvitems}
}


%------------------------------------------------

\cventry
{Web Developer} % Job title
{BoxWave Corporation} % Organization
{Kirkland, WA} % Location
{Feb. 2008 - Apr. 2008} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Hand-coded the newly designed user interface from scratch and ensured that every elements are conformed to the new specification. Ensured the newly designed website met the spec by using the latest features of HTML, CSS, ColdFusion and JavaScript.}
\end{cvitems}
}


%------------------------------------------------

\end{cventries}